Modalities for Location Virtualization

### 2022-09-20 soundness.tex
will continue on soundness tommorrwo

\section{Soundness}
\label{sec:soundness}

Our ... is an instance of Iris~\cite{iris}. This means that our logic ... is set up
via the following steps:

\begin{enumerate}
\item define a certain amount of \emph{ghost state}
      that is needed in the next two steps;
\item define a central \emph{invariant}
      that ties the machine's physical state
      to the ghost state;
\item
  define the \emph{assertions} that an end user of our ... exploits, namely
  points-to assertions that are defined as the ownership
  of a fragment of the ghost state.
\end{enumerate}

Once these steps have been carried out, Iris provides a semantic definition of
the Hoare triple $\triple\pre\instr\post$. We can then use Hoare triples to
state the reasoning rules of ...., to prove that
these rules are valid, and to state and prove the fact that ... is sound.
This is the topic of the next subsection (\sref{def:soundness:statement}).
%
After presenting these results, in \sref{sec:invariant}, we come back to the
three steps listed above and describe them at an informal level, without
diving into the concepts of Iris, which would be difficult to explain in a
thorough and concise way.
% For more information on Iris, the reader is referred to Jung \etal.'s
% paper~(\citeyear{iris}).

>>>>

\section{Implementing Logical Machinery \& Soundness}
We instantiate our program logic, $[@]$, as an instantiation of Iris~\cite{iris}, and build our modal abstractions on top of it. 
\subsection{BI-Lifting for Address Space Modality}
\label{sec:bilifting}
\mytodo{we should put some stuff here}
\subsection{Soundness}
\label{sec:soundness}
Our logic, $[@]$, operates on the machine state, which means we do not need to augment the machine state, i.e. our logical state is exact logical representation of our machine state. Consequently, we do not require an invariant, $\mathcal{I}$, except from the fact that logical/physical associated maps representing the register/memory mappings have the same domain. This ensures the correct lifting of mappings in the machine state to the \emph{assertions} that the client of our logic uses, i.e. points-to assertions that are defined as the ownership of a fragment of the logical state.

The crucial pragmatic aspect of instantiating Iris for your reasoning principles \todo{Tired stop here.} 
Once these steps have been carried out, Iris provides a semantic definition of
the Hoare triple $\triple\pre\instr\post$. We can then use Hoare triples to
state the reasoning rules of ...., to prove that
these rules are valid, and to state and prove the fact that ... is sound.
This is the topic of the next subsection (\sref{def:soundness:statement}).
%
After presenting these results, in \sref{sec:invariant}, we come back to the
three steps listed above and describe them at an informal level, without
diving into the concepts of Iris, which would be difficult to explain in a
thorough and concise way.
% For more information on Iris, the reader is referred to Jung \etal.'s
% paper~(\citeyear{iris}).
